Growing libraries of concepts with wake-sleep program induction

### 2018-07-24 talk.tex
final slide

   \underline{More human-like machine intelligence:}\\Flexibly adapting to new problem domains by
   acquiring a domain-specific language-of-thought (DSL), while jointly learning how to use the language of thought (recognition model)

>>>>

   \underline{More human-like machine intelligence}\\Flexibly adapting to new problem domains:
   acquiring a domain-specific language-of-thought (DSL); learning how to use the language of thought (recognition model)
